Article data analysis

### 2018-11-10 notebooks/article_notebook.Rmd
added figure for MIC combinations

@@

@@

test <- glm(factor(category) ~ ., data = stat_MIC, family = "binomial")

summary(test)
plot(test)
```

>>>>

## Amount of isolates resistant to specific antimicrobials
```{r}
mic_data %>%
  mutate(SMX_R = ifelse(SMX > 64, 1, 0),
         TMP_R = ifelse(TMP > 2, 1, 0),
         CIP_R = ifelse(CIP > 0.06, 1, 0),
         TET_R = ifelse(TET > 8, 1, 0),
         NAL_R = ifelse(NAL > 16, 1, 0),
         CTX_R = ifelse(CTX > 0.25, 1, 0),
         CHL_R = ifelse(CHL > 16, 1, 0),
         AMP_R = ifelse(AMP > 8, 1, 0),
         GEN_R = ifelse(GEN > 2, 1, 0)) %>%
  select(contains("_R")) %>%
  gather(AB, value) %>%
  group_by(AB) %>%
  summarise_all(funs(sum)) %>%
  arrange(desc(value)) %>%
  mutate(AB = sub("_R", "", AB))
```

@@

# Phenotypic resistance combinations
```{r, fig.width=12, fig.height=10}
mic_dotplot_data <- mic_data %>%
  mutate(SMX_R = ifelse(SMX > 64, 1, 0),
         TMP_R = ifelse(TMP > 2, 1, 0),
         CIP_R = ifelse(CIP > 0.06, 1, 0),
         TET_R = ifelse(TET > 8, 1, 0),
         NAL_R = ifelse(NAL > 16, 1, 0),
         CTX_R = ifelse(CTX > 0.25, 1, 0),
         CHL_R = ifelse(CHL > 16, 1, 0),
         AMP_R = ifelse(AMP > 8, 1, 0),
         GEN_R = ifelse(GEN > 2, 1, 0)) %>%
  select(contains("_R"), -c(CIP_R, NAL_R)) %>%
  mutate(None = ifelse(rowSums(.) == 0, 1, 0)) %>%
  group_by_all() %>%
  count() %>%
  ungroup() %>%
  mutate(id = 1:n()) %>%
  gather(AM, value, -id, -n) %>%
  mutate(value = ifelse(AM == "None" & value == 0, NA, value),
         value = ifelse(AM != "None" & value == 0, NA, value),
         AM = sub("_R", "", AM)) %>%
  filter(is.na(value) == FALSE) %>%
  mutate(AM = factor(AM, ordered = TRUE, levels = c("SMX","TMP","AMP","TET","CHL","CTX","GEN","None")))

mic_nplot_data <- mic_data %>%
  mutate(SMX_R = ifelse(SMX > 64, 1, 0),
         TMP_R = ifelse(TMP > 2, 1, 0),
         CIP_R = ifelse(CIP > 0.06, 1, 0),
         TET_R = ifelse(TET > 8, 1, 0),
         NAL_R = ifelse(NAL > 16, 1, 0),
         CTX_R = ifelse(CTX > 0.25, 1, 0),
         CHL_R = ifelse(CHL > 16, 1, 0),
         AMP_R = ifelse(AMP > 8, 1, 0),
         GEN_R = ifelse(GEN > 2, 1, 0)) %>%
  select(id, contains("_R"), -c(CIP_R, NAL_R)) %>%
  mutate(None = ifelse(rowSums(.[,2:8]) == 0, 1, 0)) %>%
  left_join(isolate_data[c("id", "species")], by = "id") %>%
  select(-id) %>%
  group_by_all() %>%
  count() %>%
  group_by_at(vars(SMX_R, TMP_R, TET_R, CTX_R, CHL_R, AMP_R, GEN_R)) %>%
  { mutate(ungroup(.), group = group_indices(.)) } %>%
  group_by(group) %>%
  mutate(group_n = sum(n))

mic_dotplot <- ggplot(mic_dotplot_data, aes(reorder(factor(id), -n), AM, fill = AM)) +
  geom_point(size = 6, pch = 21)+
  guides(fill = FALSE)+
  theme(axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid.major.x = element_line())

mic_nplot <- ggplot(mic_nplot_data, aes(reorder(factor(group), -group_n), n, fill = species))+
  geom_col(color = "black")+
  scale_fill_brewer(palette = "Paired")+
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = c(0.85,0.85),
        legend.title = element_blank())

cowplot::plot_grid(mic_nplot, mic_dotplot, ncol = 1, align = "v")

@@

# test <- glm(category ~ ., data = stat_MIC, family = "binomial")
# 
# summary(test)
# plot(test)
```
